---
title:  "Wombat Analysis Report"

output:
  html_document:
    df_print: paged
    toc: yes  
    toc_float: yes
    toc_depth: 6
  pdf_document:
    toc: yes
params:
  directory: directory
---

<style>
 table.display td { white-space: nowrap; }
 </style>

```{r, results='asis', echo=FALSE, message=FALSE, warning=FALSE, dev='pdf'}
knitr::opts_chunk$set(dpi = 120, fig.align = "center")
```

```{r, results='asis', setup, include=FALSE, dev='pdf'}
knitr::opts_knit$set(root.dir = params$directory)
```

``` {r, results='asis', echo=FALSE, message=FALSE, warning=FALSE}
if (!require('pander')) install.packages('pander', repos = "http://cran.us.r-project.org"); library('pander')
if (!require('DT')) install.packages('DT', repos = "http://cran.us.r-project.org"); library('DT')
if (!require('ape')) install.packages('ape', repos = "http://cran.us.r-project.org"); library('ape')
if (!require('plotly')) install.packages('plotly', repos = "http://cran.us.r-project.org"); library('plotly')
if (!require('rjson')) install.packages('rjson', repos = "http://cran.us.r-project.org"); library('rjson')
if (!require('viridis')) install.packages('viridis', repos = "http://cran.us.r-project.org"); library('viridis')
if (!require('scales')) install.packages('scales', repos = "http://cran.us.r-project.org"); library('scales')
if (!require('ggrepel')) install.packages('ggrepel', repos = "http://cran.us.r-project.org"); library('ggrepel')
if (!require('rmarkdown')) install.packages('rmarkdown', repos = "http://cran.us.r-project.org"); library('rmarkdown')
if (!require('cowplot')) install.packages('cowplot', repos = "http://cran.us.r-project.org"); library('cowplot')
if (!require('BiocManager')) install.packages('BiocManager', repos = "http://cran.us.r-project.org"); library('BiocManager')
if (!require('tidyverse')) install.packages('tidyverse', repos = "http://cran.us.r-project.org"); library('tidyverse')
if (!require('phytools')) install.packages('phytools', repos = "http://cran.us.r-project.org"); library('phytools')
BiocManager::install("ComplexHeatmap", force = FALSE)
library(ComplexHeatmap)
BiocManager::install("ggtree", force = FALSE)
library(ggtree)
```

```{r results='asis', warning=FALSE, message=FALSE, echo=FALSE}
# Loading the configuration file to extract parameters into the report text
wombat_config_json <- fromJSON(file = "wombat_config.json")
```

```{r results='asis', echo=FALSE, message=FALSE, warning=FALSE}
# Create a function to pass all the configuration for tables along the wombat report
Create_DT <- function(x, caption = caption, filter = "none"){
  DT::datatable(x,
                caption = caption,
                filter = filter,
                extensions = 'Buttons',
                rownames = FALSE,
                options = list(dom = 'Blfrtip',
                               buttons = c('copy', 'csv', 'excel', 'pdf'),
                               lengthMenu = list(c(10,25,50,-1),
                                                 c(10,25,50,"All"))))
}
```

##### Analysis performed on `r format(Sys.time(), '%B %d, %Y at %X')`, using [Wombat]( https://github.com/JoseBarbero/Wombat)

<br>

### Wombat's report sections {.sidebar #index}
* #### [Multi-Locus Sequence Typing (MLST)](#mlst)
* #### [Assembly analysis and annotation](#annotation)
* #### [Antibiotic resistance genes](#resistance)
* #### [Virulence genes](#virulence)
* #### [Plasmids](#plasmid)
* #### [Pangenome analysis](#pangenome)
* #### [Genomic variants](#variants)
* #### [Summary report](#summary)
* #### [How to citate](#citation)

<br>

## Multi-Locus Sequence Typing (MLST) {#mlst}
<br>
```{r results='asis', warning=FALSE, message=FALSE, echo=FALSE}
if(wombat_config_json$MLST$run_mlst == TRUE) {
  if(wombat_config_json$MLST$include_cc == TRUE) {
    cat("Following table shows the Sequence Type (ST), MLST allelic profile and Clonal Complex (CC) for each isolate using [mlst](https://github.com/tseemann/mlst).", "  \n", "<br>", "Below each column name you will find a *filter box* that you can use to filter the table by columns. You can also filter by more than one column and export this new *subset* table into a separated file (see the export buttons available).")
    MLST <- 
      read_tsv(file = "MLST/MLST_and_CC.txt", show_col_types = FALSE) %>% 
      mutate(across(where(is_character), as_factor)) %>% 
      rename(`Clonal Complex` = clonal_complex)
} else {
    cat("Following table shows the Sequence Type (ST) and MLST allelic profile for each isolate using [mlst](https://github.com/tseemann/mlst).", "  \n", "<br>", "Below each column name you will find a *filter box* that you can use to filter the table by columns. You can also filter by more than one column and export this new *subset* table into a separated file (see the export buttons available).")
    MLST <- 
      read_tsv(file = "MLST/MLST.txt", show_col_types = FALSE) %>% #Comprobar cómo queda el archivo cuando include_cc == FALSE
      mutate(across(where(is_character), as_factor))
  }
}
Create_DT(x = MLST, filter = "top", caption = '')
```
<br>
[Back to index](#index)
<br>

## Assembly analysis and annotation {#annotation}
<br>
```{r results='asis', warning=FALSE, message=FALSE, echo=FALSE}
if(wombat_config_json$annotation$annotator == "prokka") {
  pander(cat("Following table shows the number of contigs (>", toString(wombat_config_json$min_contig_len), "bp), genome length, average contig length, N50, GC content (%) and depth coverage using [SPAdes](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3342519) and annotation information using [Prokka](https://www.ncbi.nlm.nih.gov/pubmed/24642063) for each draft genome.", "  \n", "<br>", "Below each column name you will find a *filter box* that you can use to filter the table by columns. You can also filter by more than one column and export this new *subset* table into a separated file (see the export buttons available)."))
}

if(wombat_config_json$annotation$annotator == "dfast") {
  pander(cat("Following table shows the number of contigs (>", toString(wombat_config_json$min_contig_len), "bp), genome length, average contig length, N50, GC content (%) and depth coverage using [SPAdes](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3342519) and annotation information using [DFAST](https://pubmed.ncbi.nlm.nih.gov/29106469) for each draft genome.", "  \n", "<br>", "Below each column name you will find a *filter box* that you can use to filter the table by columns. You can also filter by more than one column and export this new *subset* table into a separated file (see the export buttons available)."))
}

if(wombat_config_json$annotation$run_annotation == TRUE) { 
  if(wombat_config_json$MLST$run_mlst == TRUE) {
    assembly <- read_tsv(file = "wombat_report.csv", show_col_types = FALSE) %>% 
      select(., Sample, Contigs, GenomeLen, ContigLen,	N50,	GC, ST, CDS, `Hypothetical proteins`,	CRISPRs,	rRNAs,	tRNAs) %>%
      relocate(ST, .after = tRNAs)
    if(wombat_config_json$MLST$include_cc == TRUE) {
      assembly <- read_tsv(file = "wombat_report.csv", show_col_types = FALSE) %>% 
        select(., Sample, Contigs, GenomeLen, ContigLen,	N50,	GC, ST, `clonal_complex`, CDS, `Hypothetical proteins`,	CRISPRs,	rRNAs,	tRNAs) %>%
        relocate(ST, `clonal_complex`, .after = tRNAs) %>% 
        mutate(across(where(is_character), as_factor)) %>% 
        rename(`Clonal Complex` = clonal_complex)
    }
  } else {
    assembly <- read_tsv(file = "wombat_report.csv", show_col_types = FALSE) %>% 
        select(., Sample, Contigs, GenomeLen, ContigLen,	N50,	GC, CDS, `Hypothetical proteins`,	CRISPRs,	rRNAs,	tRNAs) %>%
        mutate(across(where(is_character), as_factor))
  }
} else {
  pander(cat("Following table shows the number of contigs (>", toString(wombat_config_json$min_contig_len), "bp), genome length, average contig length, N50, GC content (%) and depth coverage using [SPAdes](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3342519) for each draft genome.", "  \n", "<br>", "Below each column name you will find a *filter box* that you can use to filter the table by columns. You can also filter by more than one column and export this new *subset* table into a separated file (see the export buttons available)."))
  if(wombat_config_json$MLST$run_mlst == TRUE) {
    assembly <- read_tsv(file = "wombat_report.csv", show_col_types = FALSE) %>%
      select(., Sample, Contigs, GenomeLen, ContigLen,	N50,	GC, ST) %>%
      relocate(ST, .after = tRNAs)
    if(wombat_config_json$MLST$include_cc == TRUE) {
      assembly <- read_tsv(file = "wombat_report.csv", show_col_types = FALSE) %>% 
        select(., Sample, Contigs, GenomeLen, ContigLen,	N50,	GC, ST, `clonal_complex`) %>%
        relocate(ST, `clonal_complex`, .after = tRNAs) %>% 
        mutate(across(where(is_character), as_factor)) %>% 
        rename(`Clonal Complex` = clonal_complex)
    }
  } else {
    assembly <- read_tsv(file = "wombat_report.csv", show_col_types = FALSE) %>% 
        select(., Sample, Contigs, GenomeLen, ContigLen,	N50,	GC) %>%
        mutate(across(where(is_character), as_factor))
  }
}
assembly$ST = as.factor(assembly$ST)
Create_DT(x = assembly, filter = "top", caption = '')
```
###############COMENTARIO IRENE: SOLO CUANDO wombat_config_json$annotation$run_annotation == TRUE deben aparecer los tabsets de CDS, hypothetical proteins, CRISPRs, rRNAs y tRNAs (generate the tabs programmatically: https://stackoverflow.com/questions/49725591/dynamically-control-number-of-tabsets-in-r-markdown, https://interludeone.com/posts/2022-03-04-programmatically-generate-tabs-in-rmarkdown/?panelset=biscoe)

  
#### Select the parameter {.tabset .tabset-fade .tabset-pills}
##### Number of contigs
```{r, echo=FALSE}
options("scipen" = 100, "digits" = 0)
if(wombat_config_json$MLST$run_mlst == TRUE) {
  Number_of_contigs <-
      ggplotly(
        ggplot(data = assembly, aes(x = Sample, y = Contigs, fill = ST)) +
          geom_bar(stat = "identity") +
          theme(panel.border = element_blank(),
                panel.background = element_rect(colour = "grey90"),
                panel.grid.minor = element_blank(),
                panel.grid.major = element_blank(),
                axis.text = element_text(size = 10),
                axis.text.x = element_text(angle = 45, hjust = 1),
                axis.title.x = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks = element_blank()) +
          labs(x = "Samples", y = "Number of contigs", title = "", fill = "ST"))
  if(wombat_config_json$MLST$include_cc == TRUE) {
    Number_of_contigs <-
      ggplotly(
        ggplot(data = assembly, aes(x = Sample, y = Contigs, fill = ST)) +
          geom_bar(stat = "identity") +
          theme(panel.border = element_blank(),
                panel.background = element_rect(colour = "grey90"),
                panel.grid.minor = element_blank(),
                panel.grid.major = element_blank(),
                axis.text = element_text(size = 10),
                axis.text.x = element_text(angle = 45, hjust = 1),
                axis.title.x = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks = element_blank()) +
          labs(x = "Samples", y = "Number of contigs", title = "", fill = "ST") +
          facet_grid(~`Clonal Complex`, scales = "free", space = "free"))
  }
} else {
  Number_of_contigs <-
    ggplotly(
      ggplot(data = assembly, aes(x = Sample, y = Contigs)) +
        geom_bar(stat = "identity") +
        theme(panel.border = element_blank(), 
              panel.background = element_rect(colour = "grey90"),
              panel.grid.minor = element_blank(),
              panel.grid.major = element_blank(),
              axis.text = element_text(size = 10),
              axis.text.x = element_text(angle = 45, hjust = 1),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank()) +
        labs(x = "Samples", y = "Number of contigs", title = ""))
}
Number_of_contigs 
```

##### Draft genome length
```{r, echo=FALSE}
options("digits" = 0)
if(wombat_config_json$MLST$run_mlst == TRUE) {
  Draft_genome_length <-
      ggplotly(
        ggplot(data = assembly, aes(x = Sample, y = GenomeLen, fill = ST)) +
          geom_bar(stat = "identity") +
          theme(panel.border = element_blank(),
                panel.background = element_rect(colour = "grey90"),
                panel.grid.minor = element_blank(),
                panel.grid.major = element_blank(),
                axis.text = element_text(size = 10),
                axis.text.x = element_text(angle = 45, hjust = 1),
                axis.title.x = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks = element_blank()) +
          labs(x = "Samples", y = "Genome lengh (bp)", title = "", fill = "ST"))
  if(wombat_config_json$MLST$include_cc == TRUE) {
    Draft_genome_length <-
      ggplotly(
        ggplot(data = assembly, aes(x = Sample, y = GenomeLen, fill = ST)) +
          geom_bar(stat = "identity") +
          theme(panel.border = element_blank(),
                panel.background = element_rect(colour = "grey90"),
                panel.grid.minor = element_blank(),
                panel.grid.major = element_blank(),
                axis.text = element_text(size = 10),
                axis.text.x = element_text(angle = 45, hjust = 1),
                axis.title.x = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks = element_blank()) +
          labs(x = "Samples", y = "Genome lengh (bp)", title = "", fill = "ST") +
          facet_grid(~`Clonal Complex`, scales = "free", space = "free"))
  }
} else {
  Draft_genome_length <-
    ggplotly(
      ggplot(data = assembly, aes(x = Sample, y = GenomeLen)) +
        geom_bar(stat = "identity") +
        theme(panel.border = element_blank(), 
              panel.background = element_rect(colour = "grey90"),
              panel.grid.minor = element_blank(),
              panel.grid.major = element_blank(),
              axis.text = element_text(size = 10),
              axis.text.x = element_text(angle = 45, hjust = 1),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank()) +
        labs(x = "Samples", y = "Genome lengh (bp)", title = ""))
}
Draft_genome_length 
```

##### Average contig length
```{r, echo=FALSE}
options("digits" = 0)
if(wombat_config_json$MLST$run_mlst == TRUE) {
  Contig_length <-
      ggplotly(
        ggplot(data = assembly, aes(x = Sample, y = ContigLen, fill = ST)) +
          geom_bar(stat = "identity") +
          theme(panel.border = element_blank(),
                panel.background = element_rect(colour = "grey90"),
                panel.grid.minor = element_blank(),
                panel.grid.major = element_blank(),
                axis.text = element_text(size = 10),
                axis.text.x = element_text(angle = 45, hjust = 1),
                axis.title.x = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks = element_blank()) +
          labs(x = "Samples", y = "Average contig length (bp)", title = "", fill = "ST"))
  if(wombat_config_json$MLST$include_cc == TRUE) {
    Contig_length <-
      ggplotly(
        ggplot(data = assembly, aes(x = Sample, y = ContigLen, fill = ST)) +
          geom_bar(stat = "identity") +
          theme(panel.border = element_blank(),
                panel.background = element_rect(colour = "grey90"),
                panel.grid.minor = element_blank(),
                panel.grid.major = element_blank(),
                axis.text = element_text(size = 10),
                axis.text.x = element_text(angle = 45, hjust = 1),
                axis.title.x = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks = element_blank()) +
          labs(x = "Samples", y = "Average contig length (bp)", title = "", fill = "ST") +
          facet_grid(~`Clonal Complex`, scales = "free", space = "free"))
  }
} else {
  Contig_length <-
    ggplotly(
      ggplot(data = assembly, aes(x = Sample, y = ContigLen)) +
        geom_bar(stat = "identity") +
        theme(panel.border = element_blank(), 
              panel.background = element_rect(colour = "grey90"),
              panel.grid.minor = element_blank(),
              panel.grid.major = element_blank(),
              axis.text = element_text(size = 10),
              axis.text.x = element_text(angle = 45, hjust = 1),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank()) +
        labs(x = "Samples", y = "Average contig length (bp)", title = ""))
}
Contig_length 
```

##### N50
```{r, echo=FALSE}
options("digits" = 0)
if(wombat_config_json$MLST$run_mlst == TRUE) {
  N50 <-
      ggplotly(
        ggplot(data = assembly, aes(x = Sample, y = N50, fill = ST)) +
          geom_bar(stat = "identity") +
          theme(panel.border = element_blank(),
                panel.background = element_rect(colour = "grey90"),
                panel.grid.minor = element_blank(),
                panel.grid.major = element_blank(),
                axis.text = element_text(size = 10),
                axis.text.x = element_text(angle = 45, hjust = 1),
                axis.title.x = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks = element_blank()) +
          labs(x = "Samples", y = "N50", title = "", fill = "ST"))
  if(wombat_config_json$MLST$include_cc == TRUE) {
    N50 <-
      ggplotly(
        ggplot(data = assembly, aes(x = Sample, y = N50, fill = ST)) +
          geom_bar(stat = "identity") +
          theme(panel.border = element_blank(),
                panel.background = element_rect(colour = "grey90"),
                panel.grid.minor = element_blank(),
                panel.grid.major = element_blank(),
                axis.text = element_text(size = 10),
                axis.text.x = element_text(angle = 45, hjust = 1),
                axis.title.x = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks = element_blank()) +
          labs(x = "Samples", y = "N50", title = "", fill = "ST") +
          facet_grid(~`Clonal Complex`, scales = "free", space = "free")) + 
          scale_y_continuous(breaks = function(x) unique(floor(pretty(seq(0, (max(x) + 1) * 1.1)))))
  }
} else {
  N50 <-
    ggplotly(
      ggplot(data = assembly, aes(x = Sample, y = N50)) +
        geom_bar(stat = "identity") +
        theme(panel.border = element_blank(), 
              panel.background = element_rect(colour = "grey90"),
              panel.grid.minor = element_blank(),
              panel.grid.major = element_blank(),
              axis.text = element_text(size = 10),
              axis.text.x = element_text(angle = 45, hjust = 1),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank()) +
        labs(x = "Samples", y = "N50", title = ""))
}
N50
```

##### GC Content
```{r, echo=FALSE}
options("scipen" = 100, "digits" = 0)
if(wombat_config_json$MLST$run_mlst == TRUE) {
  GC_content <-
      ggplotly(
        ggplot(data = assembly, aes(x = Sample, y = GC, fill = ST)) +
          geom_bar(stat = "identity") +
          theme(panel.border = element_blank(),
                panel.background = element_rect(colour = "grey90"),
                panel.grid.minor = element_blank(),
                panel.grid.major = element_blank(),
                axis.text = element_text(size = 10),
                axis.text.x = element_text(angle = 45, hjust = 1),
                axis.title.x = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks = element_blank()) +
          labs(x = "Samples", y = "GC", title = "", fill = "ST"))
  if(wombat_config_json$MLST$include_cc == TRUE) {
    GC_content <-
      ggplotly(
        ggplot(data = assembly, aes(x = Sample, y = GC, fill = ST)) +
          geom_bar(stat = "identity") +
          theme(panel.border = element_blank(),
                panel.background = element_rect(colour = "grey90"),
                panel.grid.minor = element_blank(),
                panel.grid.major = element_blank(),
                axis.text = element_text(size = 10),
                axis.text.x = element_text(angle = 45, hjust = 1),
                axis.title.x = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks = element_blank()) +
          labs(x = "Samples", y = "GC", title = "", fill = "ST") +
          facet_grid(~`Clonal Complex`, scales = "free", space = "free"))
  }
} else {
  GC_content <-
    ggplotly(
      ggplot(data = assembly, aes(x = Sample, y = GC)) +
        geom_bar(stat = "identity") +
        theme(panel.border = element_blank(), 
              panel.background = element_rect(colour = "grey90"),
              panel.grid.minor = element_blank(),
              panel.grid.major = element_blank(),
              axis.text = element_text(size = 10),
              axis.text.x = element_text(angle = 45, hjust = 1),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank()) +
        labs(x = "Samples", y = "GC", title = ""))
}
GC_content 
```

##### Number of CDS
```{r, echo=FALSE}
options("scipen" = 100, "digits" = 0)
if(wombat_config_json$MLST$run_mlst == TRUE) {
  Number_CDS <-
      ggplotly(
        ggplot(data = assembly, aes(x = Sample, y = CDS, fill = ST)) +
          geom_bar(stat = "identity") +
          theme(panel.border = element_blank(),
                panel.background = element_rect(colour = "grey90"),
                panel.grid.minor = element_blank(),
                panel.grid.major = element_blank(),
                axis.text = element_text(size = 10),
                axis.text.x = element_text(angle = 45, hjust = 1),
                axis.title.x = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks = element_blank()) +
          labs(x = "Samples", y = "Number of CDS", title = "", fill = "ST"))
  if(wombat_config_json$MLST$include_cc == TRUE) {
    Number_CDS <-
      ggplotly(
        ggplot(data = assembly, aes(x = Sample, y = CDS, fill = ST)) +
          geom_bar(stat = "identity") +
          theme(panel.border = element_blank(),
                panel.background = element_rect(colour = "grey90"),
                panel.grid.minor = element_blank(),
                panel.grid.major = element_blank(),
                axis.text = element_text(size = 10),
                axis.text.x = element_text(angle = 45, hjust = 1),
                axis.title.x = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks = element_blank()) +
          labs(x = "Samples", y = "Number of CDS", title = "", fill = "ST") +
          facet_grid(~`Clonal Complex`, scales = "free", space = "free"))
  }
} else {
  Number_CDS <-
    ggplotly(
      ggplot(data = assembly, aes(x = Sample, y = CDS)) +
        geom_bar(stat = "identity") +
        theme(panel.border = element_blank(), 
              panel.background = element_rect(colour = "grey90"),
              panel.grid.minor = element_blank(),
              panel.grid.major = element_blank(),
              axis.text = element_text(size = 10),
              axis.text.x = element_text(angle = 45, hjust = 1),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank()) +
        labs(x = "Samples", y = "Number of CDS", title = ""))
}
Number_CDS 
```

##### Hypothetical proteins
```{r, echo=FALSE}
options("scipen" = 100, "digits" = 0)
if(wombat_config_json$MLST$run_mlst == TRUE) {
  Number_hypothetical_proteins <-
      ggplotly(
        ggplot(data = assembly, aes(x = Sample, y = `Hypothetical proteins`, fill = ST)) +
          geom_bar(stat = "identity") +
          theme(panel.border = element_blank(),
                panel.background = element_rect(colour = "grey90"),
                panel.grid.minor = element_blank(),
                panel.grid.major = element_blank(),
                axis.text = element_text(size = 10),
                axis.text.x = element_text(angle = 45, hjust = 1),
                axis.title.x = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks = element_blank()) +
          labs(x = "Samples", y = "Number of hypothetical proteins", title = "", fill = "ST"))
  if(wombat_config_json$MLST$include_cc == TRUE) {
    Number_hypothetical_proteins <-
      ggplotly(
        ggplot(data = assembly, aes(x = Sample, y = `Hypothetical proteins`, fill = ST)) +
          geom_bar(stat = "identity") +
          theme(panel.border = element_blank(),
                panel.background = element_rect(colour = "grey90"),
                panel.grid.minor = element_blank(),
                panel.grid.major = element_blank(),
                axis.text = element_text(size = 10),
                axis.text.x = element_text(angle = 45, hjust = 1),
                axis.title.x = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks = element_blank()) +
          labs(x = "Samples", y = "Number of hypothetical proteins", title = "", fill = "ST") +
          facet_grid(~`Clonal Complex`, scales = "free", space = "free"))
  }
} else {
  Number_hypothetical_proteins <-
    ggplotly(
      ggplot(data = assembly, aes(x = Sample, y = `Hypothetical proteins`)) +
        geom_bar(stat = "identity") +
        theme(panel.border = element_blank(), 
              panel.background = element_rect(colour = "grey90"),
              panel.grid.minor = element_blank(),
              panel.grid.major = element_blank(),
              axis.text = element_text(size = 10),
              axis.text.x = element_text(angle = 45, hjust = 1),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank()) +
        labs(x = "Samples", y = "Number of hypothetical proteins", title = ""))
}
Number_hypothetical_proteins 
```

##### Number of CRISPRs
```{r, echo=FALSE}
options("scipen" = 100, "digits" = 0)
if(wombat_config_json$MLST$run_mlst == TRUE) {
  Number_CRISPRs <-
      ggplotly(
        ggplot(data = assembly, aes(x = Sample, y = CRISPRs, fill = ST)) +
          geom_bar(stat = "identity") +
          theme(panel.border = element_blank(),
                panel.background = element_rect(colour = "grey90"),
                panel.grid.minor = element_blank(),
                panel.grid.major = element_blank(),
                axis.text = element_text(size = 10),
                axis.text.x = element_text(angle = 45, hjust = 1),
                axis.title.x = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks = element_blank()) +
          labs(x = "Samples", y = "Number of CRISPRs", title = "", fill = "ST") + 
          scale_y_continuous(breaks = function(x) unique(floor(pretty(seq(0, (max(x) + 1) * 1.1))))))
}
  if(wombat_config_json$MLST$include_cc == TRUE) {
    Number_CRISPRs <-
      ggplotly(
        ggplot(data = assembly, aes(x = Sample, y = CRISPRs, fill = ST)) +
          geom_bar(stat = "identity") +
          theme(panel.border = element_blank(),
                panel.background = element_rect(colour = "grey90"),
                panel.grid.minor = element_blank(),
                panel.grid.major = element_blank(),
                axis.text = element_text(size = 10),
                axis.text.x = element_text(angle = 45, hjust = 1),
                axis.title.x = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks = element_blank()) +
          labs(x = "Samples", y = "Number of CRISPRs", title = "", fill = "ST") +
          facet_grid(~`Clonal Complex`, scales = "free", space = "free") + 
          scale_y_continuous(breaks = function(x) unique(floor(pretty(seq(0, (max(x) + 1) * 1.1))))))
} else {
  Number_CRISPRs <-
    ggplotly(
      ggplot(data = assembly, aes(x = Sample, y = CRISPRs)) +
        geom_bar(stat = "identity") +
        theme(panel.border = element_blank(), 
              panel.background = element_rect(colour = "grey90"),
              panel.grid.minor = element_blank(),
              panel.grid.major = element_blank(),
              axis.text = element_text(size = 10),
              axis.text.x = element_text(angle = 45, hjust = 1),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank()) +
        labs(x = "Samples", y = "Number of CRISPRs", title = "") + 
        scale_y_continuous(breaks = function(x) unique(floor(pretty(seq(0, (max(x) + 1) * 1.1))))))
}
Number_CRISPRs
```

##### Number of rRNAs
```{r, echo=FALSE}
options("scipen" = 100, "digits" = 0)
if(wombat_config_json$MLST$run_mlst == TRUE) {
  Number_rRNAs <-
      ggplotly(
        ggplot(data = assembly, aes(x = Sample, y = rRNAs, fill = ST)) +
          geom_bar(stat = "identity") +
          theme(panel.border = element_blank(),
                panel.background = element_rect(colour = "grey90"),
                panel.grid.minor = element_blank(),
                panel.grid.major = element_blank(),
                axis.text = element_text(size = 10),
                axis.text.x = element_text(angle = 45, hjust = 1),
                axis.title.x = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks = element_blank()) +
          labs(x = "Samples", y = "Number of rRNAs", title = "", fill = "ST"))
  if(wombat_config_json$MLST$include_cc == TRUE) {
    Number_rRNAs <-
      ggplotly(
        ggplot(data = assembly, aes(x = Sample, y = rRNAs, fill = ST)) +
          geom_bar(stat = "identity") +
          theme(panel.border = element_blank(),
                panel.background = element_rect(colour = "grey90"),
                panel.grid.minor = element_blank(),
                panel.grid.major = element_blank(),
                axis.text = element_text(size = 10),
                axis.text.x = element_text(angle = 45, hjust = 1),
                axis.title.x = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks = element_blank()) +
          labs(x = "Samples", y = "Number of rRNAs", title = "", fill = "ST") +
          facet_grid(~`Clonal Complex`, scales = "free", space = "free"))
  }
} else {
  Number_rRNAs <-
    ggplotly(
      ggplot(data = assembly, aes(x = Sample, y = rRNAs)) +
        geom_bar(stat = "identity") +
        theme(panel.border = element_blank(), 
              panel.background = element_rect(colour = "grey90"),
              panel.grid.minor = element_blank(),
              panel.grid.major = element_blank(),
              axis.text = element_text(size = 10),
              axis.text.x = element_text(angle = 45, hjust = 1),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank()) +
        labs(x = "Samples", y = "Number of rRNAs", title = ""))
}
Number_rRNAs
```

##### Number of tRNAs
```{r, echo=FALSE}
options("scipen" = 100, "digits" = 0)
if(wombat_config_json$MLST$run_mlst == TRUE) {
  Number_tRNAs <-
      ggplotly(
        ggplot(data = assembly, aes(x = Sample, y = tRNAs, fill = ST)) +
          geom_bar(stat = "identity") +
          theme(panel.border = element_blank(),
                panel.background = element_rect(colour = "grey90"),
                panel.grid.minor = element_blank(),
                panel.grid.major = element_blank(),
                axis.text = element_text(size = 10),
                axis.text.x = element_text(angle = 45, hjust = 1),
                axis.title.x = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks = element_blank()) +
          labs(x = "Samples", y = "Number of tRNAs", title = "", fill = "ST"))
  if(wombat_config_json$MLST$include_cc == TRUE) {
    Number_tRNAs <-
      ggplotly(
        ggplot(data = assembly, aes(x = Sample, y = tRNAs, fill = ST)) +
          geom_bar(stat = "identity") +
          theme(panel.border = element_blank(),
                panel.background = element_rect(colour = "grey90"),
                panel.grid.minor = element_blank(),
                panel.grid.major = element_blank(),
                axis.text = element_text(size = 10),
                axis.text.x = element_text(angle = 45, hjust = 1),
                axis.title.x = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks = element_blank()) +
          labs(x = "Samples", y = "Number of tRNAs", title = "", fill = "ST") +
          facet_grid(~`Clonal Complex`, scales = "free", space = "free"))
  }
} else {
  Number_tRNAs <-
    ggplotly(
      ggplot(data = assembly, aes(x = Sample, y = tRNAs)) +
        geom_bar(stat = "identity") +
        theme(panel.border = element_blank(), 
              panel.background = element_rect(colour = "grey90"),
              panel.grid.minor = element_blank(),
              panel.grid.major = element_blank(),
              axis.text = element_text(size = 10),
              axis.text.x = element_text(angle = 45, hjust = 1),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank()) +
        labs(x = "Samples", y = "Number of tRNAs", title = ""))
}
Number_tRNAs
```
<br>

[Back to index](#index)

## Antibiotic resistance genes {#resistance}
<br>
```{r results='asis', warning=FALSE, message=FALSE, echo=FALSE}
if(wombat_config_json$antimicrobial_resistance_genes$run_antimicrobial_resistance_genes_prediction == TRUE) {
  if('amrfinder' %in% wombat_config_json$antimicrobial_resistance_genes$antimicrobial_resistance_genes_predictor_tool) {
    pander(cat("Following table shows antibiotic resistance genes by screening the draft genomes against the [Pathogen Detection Reference Gene Catalog]( https://www.ncbi.nlm.nih.gov/pathogens/isolates#/refgene) by using [AMRFinderPlus](https://www.ncbi.nlm.nih.gov/pathogens/antimicrobial-resistance/AMRFinder). Any hit with coverage below", toString(wombat_config_json$antimicrobial_resistance_genes$amrfinder$mincov), "% and identity below", toString(wombat_config_json$antimicrobial_resistance_genes$amrfinder$minid), "% was removed.", "  \n", "<br>", "Below each column name you will find a *filter box* that you can use to filter the table by columns. You can also filter by more than one column and export this new *subset* table into a separated file (see the export buttons available)."))
  }
}

if(wombat_config_json$antimicrobial_resistance_genes$run_antimicrobial_resistance_genes_prediction == TRUE) {
  if('amrfinder' %in% wombat_config_json$antimicrobial_resistance_genes$antimicrobial_resistance_genes_predictor_tool) {    
    AMR <- 
      read_tsv(file = "Antimicrobial_resistance_genes/AMRFinder/AMR_AMRFinder.tsv", show_col_types = FALSE) %>% 
      mutate(across(where(is_character), as_factor)) %>% 
      filter(`Element type` == "AMR" & `Element subtype` != "POINT") %>% 
      select(-c("Scope", "Element type", "Element subtype", "Method", "Target length", "Reference sequence length", "Alignment length", "Accession of closest sequence", "Name of closest sequence", "HMM id", "HMM description"))
  }
}
Create_DT(x = AMR, filter = "top", caption = '')

if(wombat_config_json$antimicrobial_resistance_genes$run_antimicrobial_resistance_genes_prediction == TRUE) {
  if('amrfinder' %in% wombat_config_json$antimicrobial_resistance_genes$antimicrobial_resistance_genes_predictor_tool) {
    pander(cat("<br>", "Following figure represents presence/absence of antibiotic resistance genes in each draft genome against the [Pathogen Detection Reference Gene Catalog]( https://www.ncbi.nlm.nih.gov/pathogens/isolates#/refgene) by using [AMRFinderPlus](https://www.ncbi.nlm.nih.gov/pathogens/antimicrobial-resistance/AMRFinder). Presence is represented as minimum coverage of", toString(wombat_config_json$antimicrobial_resistance_genes$amrfinder$mincov),  "% and minimum identity of", toString(wombat_config_json$antimicrobial_resistance_genes$amrfinder$minid), "%.", "<br>"))
  }
}
```

```{r results='asis', warning=FALSE, message=FALSE, echo=FALSE, dpi = 80}
if(wombat_config_json$antimicrobial_resistance_genes$run_antimicrobial_resistance_genes_prediction == TRUE) {
  if('amrfinder' %in% wombat_config_json$antimicrobial_resistance_genes$antimicrobial_resistance_genes_predictor_tool) {
    AMR_matrix <- 
      read_tsv(file = "Antimicrobial_resistance_genes/AMRFinder/AMR_genes_AMRFinder_matrix.tsv", show_col_types = FALSE) %>% 
      pivot_longer(data = ., cols = !c(Sample, DATABASE), names_to = "Resistance Class", values_to = "Gene symbol") %>%
      mutate(.data = ., "Presence / Absence" = as.numeric(!str_detect(`Gene symbol`, "^-$"))) %>%
      mutate(across(where(is_character), as_factor))
    
    resistance_class_annotation <- AMR_matrix[, c("Resistance Class", "Gene symbol")] %>% 
    distinct() %>% 
    filter(`Gene symbol` != "-") %>%
    select(c("Resistance Class")) %>%
    as.data.frame

    if(wombat_config_json$MLST$run_mlst == TRUE) {
      AMR_matrix <- AMR_matrix  %>% 
          left_join(x = ., y = MLST %>% select(Sample, ST), by = "Sample")
        
        mlst_annotation <- MLST %>% 
          select(., ST) %>%
          mutate(across(c(ST),
                        factor))  %>%
          as.data.frame

        AMR_heatmap <- AMR_matrix %>%
          select(c(Sample, `Gene symbol`, `Presence / Absence`)) %>%
          pivot_wider(data = ., names_from = `Gene symbol`, values_from = `Presence / Absence`, values_fill = 0) %>% 
          select(., -`-`) %>%
          remove_rownames %>% 
          column_to_rownames(var="Sample") %>% 
          base::as.matrix() %>%  
          Heatmap(.,
                  name = " ",
                  col = colorRampPalette(c("#F8696B", "#63BE7B"))(2),
                  cluster_rows = FALSE,
                  cluster_columns = FALSE,
                  top_annotation = HeatmapAnnotation(df = resistance_class_annotation,
                                                     which = "col", 
                                                     simple_anno_size = unit(4, "mm"), 
                                                     annotation_name_side = "left", 
                                                     gap = unit(1, 'mm')), 
                  left_annotation = HeatmapAnnotation(df = mlst_annotation,
                                                      which = "row",
                                                      simple_anno_size = unit(4, "mm"),
                                                      annotation_name_side = "bottom",
                                                      gap = unit(0.5, 'mm')),
                  heatmap_legend_param = list(at = c(1, 0), 
                                              labels = c("Presence", "Absence"),
                                              title = " ",
                                              color_bar = "discrete"))

      if(wombat_config_json$MLST$include_cc == TRUE) {
        AMR_matrix <- AMR_matrix  %>% 
          left_join(x = ., y = MLST %>% select(Sample, ST, `Clonal Complex`), by = "Sample")
        
        mlst_annotation <- MLST %>% 
          select(., ST, `Clonal Complex`) %>%
          mutate(across(c(ST),
                        factor))  %>%
          as.data.frame

        AMR_heatmap <- AMR_matrix %>%
          select(c(Sample, `Gene symbol`, `Presence / Absence`)) %>%
          pivot_wider(data = ., names_from = `Gene symbol`, values_from = `Presence / Absence`, values_fill = 0) %>% 
          select(., -`-`) %>%
          remove_rownames %>% 
          column_to_rownames(var="Sample") %>% 
          base::as.matrix() %>%  
          Heatmap(.,
                  name = " ",
                  col = colorRampPalette(c("#F8696B", "#63BE7B"))(2),
                  cluster_rows = FALSE,
                  cluster_columns = FALSE,
                  top_annotation = HeatmapAnnotation(df = resistance_class_annotation,
                                                     which = "col", 
                                                     simple_anno_size = unit(4, "mm"), 
                                                     annotation_name_side = "left", 
                                                     gap = unit(1, 'mm')), 
                  left_annotation = HeatmapAnnotation(df = mlst_annotation,
                                                      which = "row",
                                                      simple_anno_size = unit(4, "mm"),
                                                      annotation_name_side = "bottom",
                                                      gap = unit(0.5, 'mm')),
                  heatmap_legend_param = list(at = c(1, 0), 
                                              labels = c("Presence", "Absence"),
                                              title = " ",
                                              color_bar = "discrete"))
      }
    } else {
      AMR_heatmap <- AMR_matrix %>%
        select(c(Sample, `Gene symbol`, `Presence / Absence`)) %>%
        pivot_wider(data = ., names_from = `Gene symbol`, values_from = `Presence / Absence`, values_fill = 0) %>% 
        select(., -`-`) %>%
        remove_rownames %>% 
        column_to_rownames(var="Sample") %>% 
        base::as.matrix() %>%  
        Heatmap(.,
                name = " ",
                col = colorRampPalette(c("#F8696B", "#63BE7B"))(2),
                cluster_rows = FALSE,
                cluster_columns = FALSE,
                top_annotation = HeatmapAnnotation(df = resistance_class_annotation,
                                                   which = "col", 
                                                   simple_anno_size = unit(4, "mm"), 
                                                   annotation_name_side = "left", 
                                                   gap = unit(1, 'mm')), 
                heatmap_legend_param = list(at = c(1, 0), 
                                            labels = c("Presence", "Absence"),
                                            title = " ",
                                            color_bar = "discrete"))
    }
    AMR_heatmap
  }
}
```
<br>

#### Point mutations conferring antibiotic resistance
```{r results='asis', warning=FALSE, message=FALSE, echo=FALSE}
if(wombat_config_json$antimicrobial_resistance_genes$run_antimicrobial_resistance_genes_prediction == TRUE) {
  if('amrfinder' %in% wombat_config_json$antimicrobial_resistance_genes$antimicrobial_resistance_genes_predictor_tool) {
    pander(cat("<br>", "Following table shows known point mutations by screening the draft genomes against the [Pathogen Detection Reference Gene Catalog]( https://www.ncbi.nlm.nih.gov/pathogens/isolates#/refgene) by using [AMRFinderPlus]( https://www.ncbi.nlm.nih.gov/pathogens/antimicrobial-resistance/AMRFinder). Any hit with coverage below", toString(wombat_config_json$antimicrobial_resistance_genes$amrfinder$mincov), "% and identity below", toString(wombat_config_json$antimicrobial_resistance_genes$amrfinder$minid), "% was removed.", "  \n", "<br>", "Below each column name you will find a *filter box* that you can use to filter the table by columns. You can also filter by more than one column and export this new *subset* table into a separated file (see the export buttons available)."))
  }
}
    
if(wombat_config_json$antimicrobial_resistance_genes$run_antimicrobial_resistance_genes_prediction == TRUE) {
  if('amrfinder' %in% wombat_config_json$antimicrobial_resistance_genes$antimicrobial_resistance_genes_predictor_tool) {
    AMR_pmut <- 
      read_tsv(file = "Antimicrobial_resistance_genes/AMRFinder/AMR_AMRFinder.tsv", show_col_types = FALSE) %>% 
      mutate(across(where(is_character), as_factor)) %>% 
      filter(`Element subtype` == "POINT" ) %>% 
      select(-c("Scope", "Element type", "Element subtype", "Method", "Target length", "Reference sequence length", "Alignment length", "Accession of closest sequence", "Name of closest sequence", "HMM id", "HMM description"))
    
    Create_DT(x = AMR_pmut, filter = "top", caption = '')
  }
}

if(wombat_config_json$antimicrobial_resistance_genes$run_antimicrobial_resistance_genes_prediction == TRUE) {
  if('amrfinder' %in% wombat_config_json$antimicrobial_resistance_genes$antimicrobial_resistance_genes_predictor_tool) {
    pander(cat("<br>", "Following figure represents known point mutations in each draft genome by using [AMRFinderPlus]( https://www.ncbi.nlm.nih.gov/pathogens/antimicrobial-resistance/AMRFinder). Presence is represented as minimum coverage of", toString(wombat_config_json$antimicrobial_resistance_genes$amrfinder$mincov),  "% and minimum identity of", toString(wombat_config_json$antimicrobial_resistance_genes$amrfinder$minid), "%."))
  }
}
```
  
```{r results='asis', warning=FALSE, message=FALSE, echo=FALSE, dpi = 80}
if(wombat_config_json$antimicrobial_resistance_genes$run_antimicrobial_resistance_genes_prediction == TRUE) {
  if('amrfinder' %in% wombat_config_json$antimicrobial_resistance_genes$antimicrobial_resistance_genes_predictor_tool) {
    AMR_pmut_matrix <- 
      read_tsv(file = "Antimicrobial_resistance_genes/AMRFinder/AMR_point_mutations_AMRFinder_matrix.tsv", show_col_types = FALSE) %>%
      pivot_longer(data = ., cols = !c(Sample), names_to = "Resistance Class", values_to = "Point mutation") %>%
      mutate(.data = ., "Presence / Absence" = as.numeric(!str_detect(`Point mutation`, "^-$"))) %>%
      mutate(`Point mutation` = strsplit(as.character(`Point mutation`), ",")) %>% 
      unnest(`Point mutation`) %>%
      mutate(across(where(is_character), as_factor))

    resistance_class_pmut_annotation <- AMR_pmut_matrix[, c("Resistance Class", "Point mutation")] %>%
      distinct() %>% 
      filter(`Point mutation` != "-") %>%
      select(c("Resistance Class")) %>%
      as.data.frame
    
    if(wombat_config_json$MLST$run_mlst == TRUE) {
      AMR_pmut_matrix <- AMR_pmut_matrix  %>% 
          left_join(x = ., y = MLST %>% select(Sample, ST), by = "Sample")
      
        pmut_heatmap <- AMR_pmut_matrix %>%
          select(c(Sample, `Point mutation`, `Presence / Absence`)) %>%
          distinct() %>%
          pivot_wider(data = ., names_from = `Point mutation`, values_from = `Presence / Absence`, values_fill = 0) %>%
          select(., -`-`) %>%
          column_to_rownames(var="Sample") %>% 
          base::as.matrix() %>%  
          Heatmap(.,
                  name = " ",
                  col = colorRampPalette(c("#F8696B", "#63BE7B"))(2),
                  cluster_rows = FALSE,
                  cluster_columns = FALSE,
                  top_annotation = HeatmapAnnotation(df = resistance_class_pmut_annotation,
                                                     which = "col",
                                                     simple_anno_size = unit(4, "mm"),
                                                     annotation_name_side = "left",
                                                     gap = unit(1, 'mm')),
                  left_annotation = HeatmapAnnotation(df = mlst_annotation,
                                                      which = "row",
                                                      simple_anno_size = unit(4, "mm"),
                                                      annotation_name_side = "bottom",
                                                      gap = unit(0.5, 'mm')),
                  heatmap_legend_param = list(at = c(1, 0), 
                                              labels = c("Presence", "Absence"),
                                              title = " ",
                                              color_bar = "discrete"))
      
      if(wombat_config_json$MLST$include_cc == TRUE) {
        AMR_pmut_matrix <- AMR_pmut_matrix  %>% 
          left_join(x = ., y = MLST %>% select(Sample, ST, `Clonal Complex`), by = "Sample")
      
        pmut_heatmap <- AMR_pmut_matrix %>%
          select(c(Sample, `Point mutation`, `Presence / Absence`)) %>%
          distinct() %>%
          pivot_wider(data = ., names_from = `Point mutation`, values_from = `Presence / Absence`, values_fill = 0) %>%
          select(., -`-`) %>%
          column_to_rownames(var="Sample") %>% 
          base::as.matrix() %>%  
          Heatmap(.,
                  name = " ",
                  col = colorRampPalette(c("#F8696B", "#63BE7B"))(2),
                  cluster_rows = FALSE,
                  cluster_columns = FALSE,
                  top_annotation = HeatmapAnnotation(df = resistance_class_pmut_annotation,
                                                     which = "col",
                                                     simple_anno_size = unit(4, "mm"),
                                                     annotation_name_side = "left",
                                                     gap = unit(1, 'mm')),
                  left_annotation = HeatmapAnnotation(df = mlst_annotation,
                                                      which = "row",
                                                      simple_anno_size = unit(4, "mm"),
                                                      annotation_name_side = "bottom",
                                                      gap = unit(0.5, 'mm')),
                  heatmap_legend_param = list(at = c(1, 0), 
                                              labels = c("Presence", "Absence"),
                                              title = " ",
                                              color_bar = "discrete"))
      }
    } else {
      pmut_heatmap <- AMR_pmut_matrix %>%
        select(c(Sample, `Point mutation`, `Presence / Absence`)) %>%
        distinct() %>%
        pivot_wider(data = ., names_from = `Point mutation`, values_from = `Presence / Absence`, values_fill = 0) %>%
        select(., -`-`) %>%
        column_to_rownames(var="Sample") %>% 
        base::as.matrix() %>%  
        Heatmap(.,
                name = " ",
                col = colorRampPalette(c("#F8696B", "#63BE7B"))(2),
                cluster_rows = FALSE,
                cluster_columns = FALSE,
                top_annotation = HeatmapAnnotation(df = resistance_class_pmut_annotation,
                                                   which = "col",
                                                   simple_anno_size = unit(4, "mm"),
                                                   annotation_name_side = "left",
                                                   gap = unit(1, 'mm')),
                heatmap_legend_param = list(at = c(1, 0), 
                                            labels = c("Presence", "Absence"),
                                            title = " ",
                                            color_bar = "discrete"))
    }
    pmut_heatmap
  }
}
```

```{r results='asis', warning=FALSE, message=FALSE, echo=FALSE}
if(wombat_config_json$antimicrobial_resistance_genes$run_antimicrobial_resistance_genes_prediction == TRUE) {
  if('abricate' %in% wombat_config_json$antimicrobial_resistance_genes$antimicrobial_resistance_genes_predictor_tool) {
    pander(cat("Following table(s) show(s) antibiotic resistance genes by screening the draft genomes against the selected database(s) by using [ABRicate](https://github.com/tseemann/abricate). Any hit with coverage below", toString(wombat_config_json$antimicrobial_resistance_genes$abricate$mincov), "% and identity below", toString(wombat_config_json$antimicrobial_resistance_genes$amrfinder$minid), "% was removed.", "  \n", "<br>", "Below each column name you will find a *filter box* that you can use to filter the table by columns. You can also filter by more than one column and export this new *subset* table into a separated file (see the export buttons available)."))
  }
}
```
<br>

#El botón (tabset) solo debe aparecer para cada base de datos de wombat_config_json$antimicrobial_resistance_genes$abricate$antimicrobial_resistance_databases

#### Select the database {.tabset .tabset-fade .tabset-pills}
##### argannot
```{r, results='asis', echo=FALSE}
options("scipen" = 100, "digits" = 0)
if(wombat_config_json$antimicrobial_resistance_genes$run_antimicrobial_resistance_genes_prediction == TRUE) {
  if('argannot' %in% wombat_config_json$antimicrobial_resistance_genes$abricate$antimicrobial_resistance_databases) {
    Anti_Res_Genes <- 
      read_tsv(file = "Antimicrobial_resistance_genes/ABRicate/AMR_ABRicate.tsv", show_col_types = FALSE) %>% 
      select(!c("COVERAGE", "COVERAGE_MAP")) %>% 
      filter(`DATABASE` == "argannot" ) %>% 
      select(!c("DATABASE")) %>% 
      select_if(function(x) !(all(is.na(x)) | all(x==""))) %>%
      mutate(across(where(is_character), as_factor))
    Create_DT(x = Anti_Res_Genes, filter = "top", caption = '')
  }
}
```

##### CARD
```{r, results='asis', echo=FALSE}
options("scipen" = 100, "digits" = 0)
if(wombat_config_json$antimicrobial_resistance_genes$run_antimicrobial_resistance_genes_prediction == TRUE) {
  if('card' %in% wombat_config_json$antimicrobial_resistance_genes$abricate$antimicrobial_resistance_databases) {
    Anti_Res_Genes <- 
      read_tsv(file = "Antimicrobial_resistance_genes/ABRicate/AMR_ABRicate.tsv", show_col_types = FALSE) %>% 
      select(!c("COVERAGE", "COVERAGE_MAP")) %>% 
      filter(`DATABASE` == "card" ) %>% 
      select(!c("DATABASE")) %>% 
      select_if(function(x) !(all(is.na(x)) | all(x==""))) %>%
      mutate(across(where(is_character), as_factor))
    Create_DT(x = Anti_Res_Genes, filter = "top", caption = '')
  }
}
```

##### Ecoh
```{r, results='asis', echo=FALSE}
options("scipen" = 100, "digits" = 0)
if(wombat_config_json$antimicrobial_resistance_genes$run_antimicrobial_resistance_genes_prediction == TRUE) {
  if('ecoh' %in% wombat_config_json$antimicrobial_resistance_genes$abricate$antimicrobial_resistance_databases) {
    Anti_Res_Genes <- 
      read_tsv(file = "Antimicrobial_resistance_genes/ABRicate/AMR_ABRicate.tsv", show_col_types = FALSE) %>% 
      select(!c("COVERAGE", "COVERAGE_MAP")) %>% 
      filter(`DATABASE` == "ecoh" ) %>% 
      select(!c("DATABASE")) %>% 
      select_if(function(x) !(all(is.na(x)) | all(x==""))) %>%
      mutate(across(where(is_character), as_factor))
    Create_DT(x = Anti_Res_Genes, filter = "top", caption = '')
  }
}
```

##### Megares
```{r, results='asis', echo=FALSE}
options("scipen" = 100, "digits" = 0)
if(wombat_config_json$antimicrobial_resistance_genes$run_antimicrobial_resistance_genes_prediction == TRUE) {
  if('megares' %in% wombat_config_json$antimicrobial_resistance_genes$abricate$antimicrobial_resistance_databases) {
    Anti_Res_Genes <- 
      read_tsv(file = "Antimicrobial_resistance_genes/ABRicate/AMR_ABRicate.tsv", show_col_types = FALSE) %>% 
      select(!c("COVERAGE", "COVERAGE_MAP")) %>% 
      filter(`DATABASE` == "megares" ) %>% 
      select(!c("DATABASE")) %>% 
      select_if(function(x) !(all(is.na(x)) | all(x==""))) %>%
      mutate(across(where(is_character), as_factor))
    Create_DT(x = Anti_Res_Genes, filter = "top", caption = '')
  }
}
```

##### NCBI
```{r, results='asis', echo=FALSE}
options("scipen" = 100, "digits" = 0)
if(wombat_config_json$antimicrobial_resistance_genes$run_antimicrobial_resistance_genes_prediction == TRUE) {
  if('ncbi' %in% wombat_config_json$antimicrobial_resistance_genes$abricate$antimicrobial_resistance_databases) {
    Anti_Res_Genes <- 
      read_tsv(file = "Antimicrobial_resistance_genes/ABRicate/AMR_ABRicate.tsv", show_col_types = FALSE) %>% 
      select(!c("COVERAGE", "COVERAGE_MAP")) %>% 
      filter(`DATABASE` == "ncbi" ) %>% 
      select(!c("DATABASE")) %>% 
      select_if(function(x) !(all(is.na(x)) | all(x==""))) %>% 
      mutate(across(where(is_character), as_factor))
    Create_DT(x = Anti_Res_Genes, filter = "top", caption = '')
  }
}
```

##### Resfinder
```{r, results='asis', echo=FALSE}
options("scipen" = 100, "digits" = 0)
if(wombat_config_json$antimicrobial_resistance_genes$run_antimicrobial_resistance_genes_prediction == TRUE) {
  if('resfinder' %in% wombat_config_json$antimicrobial_resistance_genes$abricate$antimicrobial_resistance_databases) {
    Anti_Res_Genes <- 
      read_tsv(file = "Antimicrobial_resistance_genes/ABRicate/AMR_ABRicate.tsv", show_col_types = FALSE) %>% 
      select(!c("COVERAGE", "COVERAGE_MAP")) %>% 
      filter(`DATABASE` == "resfinder" ) %>% 
      select(!c("DATABASE")) %>% 
      select_if(function(x) !(all(is.na(x)) | all(x==""))) %>% 
      mutate(across(where(is_character), as_factor))
    Create_DT(x = Anti_Res_Genes, filter = "top", caption = '')
  }
}
```
<br>

## {-}

```{r results='asis', warning=FALSE, message=FALSE, echo=FALSE}
if(wombat_config_json$antimicrobial_resistance_genes$run_antimicrobial_resistance_genes_prediction == TRUE) {
  if('abricate' %in% wombat_config_json$antimicrobial_resistance_genes$antimicrobial_resistance_genes_predictor_tool) {
    pander(cat("<br>", "Following figure(s) represent(s) presence/absence of antibiotic resistance genes in each draft genome against the selected database(s) by using [ABRicate](https://github.com/tseemann/abricate). Presence is represented as minimum coverage of", toString(wombat_config_json$antimicrobial_resistance_genes$abricate$mincov),  "% and minimum identity of", toString(wombat_config_json$antimicrobial_resistance_genes$abricate$minid), "%.", "<br>"))
  }
}
```
<br>

#### Select the database {.tabset .tabset-fade .tabset-pills}

```{r results='asis', warning=FALSE, message=FALSE, echo=FALSE, fig.align='left', fig.width=10, fig.height=5}

if(wombat_config_json$antimicrobial_resistance_genes$run_antimicrobial_resistance_genes_prediction == TRUE) {
  if('abricate' %in% wombat_config_json$antimicrobial_resistance_genes$antimicrobial_resistance_genes_predictor_tool) {
    Anti_Res_Genes_PA <- 
      read_tsv(file = "Antimicrobial_resistance_genes/ABRicate/AMR_genes_ABRicate_matrix.tsv", show_col_types = FALSE) %>% 
      slice(-n())
    
    DBs <- levels(factor(Anti_Res_Genes_PA$DATABASE))
    
    for (i in seq_along(DBs)) {
      cat('#####',DBs[i],' \n')
      Anti_Res_Genes_PA.i <- NULL
      Anti_Res_Genes_PA.i_data <- Anti_Res_Genes_PA[Anti_Res_Genes_PA$DATABASE == DBs[i],]
      Anti_Res_Genes_PA.i <- subset(Anti_Res_Genes_PA.i_data, select = -c(RESISTANCE, DATABASE))
      Anti_Res_Genes_PA.i <- as.data.frame(Anti_Res_Genes_PA.i)
      rownames(Anti_Res_Genes_PA.i) <- Anti_Res_Genes_PA.i$Gene
      Anti_Res_Genes_PA.i$Gene <- NULL
      Anti_Res_Genes_matrix <- t(as.matrix(Anti_Res_Genes_PA.i))
      
      resistance_class_annotation <- Anti_Res_Genes_PA.i_data[, c("Gene", "RESISTANCE")] %>% 
        select(c("RESISTANCE")) %>%
        as.data.frame
      
      if(DBs[i] == "card" | DBs[i] == "ncbi"){
        top_annotation = HeatmapAnnotation(df = resistance_class_annotation, #que solo aparezca esta anotación cuando DBs = card or ncbi.
                                                    which = "col", 
                                                    simple_anno_size = unit(4, "mm"), 
                                                    annotation_name_side = "left", 
                                                    gap = unit(1, 'mm'))
      } else {
        top_annotation = NULL
      }
      
      if(wombat_config_json$MLST$run_mlst == TRUE) {
        if(wombat_config_json$MLST$include_cc == TRUE) {
          Anti_Res_Genes_matrix <- as.data.frame(Anti_Res_Genes_matrix)
          Anti_Res_Genes_matrix <- tibble::rownames_to_column(Anti_Res_Genes_matrix, "Sample")
        
          Anti_Res_Genes_matrix_mlst <- Anti_Res_Genes_matrix  %>% 
            left_join(x = ., y = MLST %>% select(Sample, ST, `Clonal Complex`), by = "Sample")

          mlst_annotation <- Anti_Res_Genes_matrix_mlst %>% 
            select(., ST, `Clonal Complex`) %>%
            mutate(across(c(ST),
                          factor))  %>%
            as.data.frame
        
          Anti_Res_Genes_matrix <- as.data.frame(Anti_Res_Genes_matrix)
          rownames(Anti_Res_Genes_matrix) <- Anti_Res_Genes_matrix$Sample
          Anti_Res_Genes_matrix$Sample <- NULL
          
          draw(
            Heatmap(Anti_Res_Genes_matrix, 
                    width = ncol(Anti_Res_Genes_matrix)*unit(4, "mm"), 
                    height = nrow(Anti_Res_Genes_matrix)*unit(4, "mm"),  
                    column_title = paste("Database = ", DBs[i], sep = ""),
                    col = colorRampPalette(c("#F8696B", "#63BE7B"))(2),
                    cluster_rows = FALSE,
                    cluster_columns = FALSE,
                    top_annotation = top_annotation, 
                    left_annotation = HeatmapAnnotation(df = mlst_annotation,
                                                        which = "row",
                                                        simple_anno_size = unit(4, "mm"),
                                                        annotation_name_side = "bottom",
                                                        gap = unit(0.5, 'mm')),
                    heatmap_legend_param = list(at = c(1, 0), 
                                                labels = c("Presence", "Absence"),
                                                title = " ",
                                                color_bar = "discrete")
          ))
        } else { 
          Anti_Res_Genes_matrix <- as.data.frame(Anti_Res_Genes_matrix)
        Anti_Res_Genes_matrix <- tibble::rownames_to_column(Anti_Res_Genes_matrix, "Sample")
        
        Anti_Res_Genes_matrix_mlst <- Anti_Res_Genes_matrix  %>% 
          left_join(x = ., y = MLST %>% select(Sample, ST), by = "Sample")

        mlst_annotation <- Anti_Res_Genes_matrix_mlst %>% 
          select(., ST) %>%
          mutate(across(c(ST),
                        factor))  %>%
          as.data.frame
        
        Anti_Res_Genes_matrix <- as.data.frame(Anti_Res_Genes_matrix)
          rownames(Anti_Res_Genes_matrix) <- Anti_Res_Genes_matrix$Sample
          Anti_Res_Genes_matrix$Sample <- NULL
          
          #COMENTARIO IRENE: top_annotation solo debe aparecer cuando DBs[i] = card or ncbi
          if(DBs[i] == "card" | DBs[i] == "ncbi"){
            top_annotation = HeatmapAnnotation(df = resistance_class_annotation, #que solo aparezca esta anotación cuando DBs = card or ncbi.
                                                       which = "col", 
                                                       simple_anno_size = unit(4, "mm"), 
                                                       annotation_name_side = "left", 
                                                       gap = unit(1, 'mm'))
          } else {
            top_annotation = NULL
          }

          draw(
            Heatmap(Anti_Res_Genes_matrix, 
                    width = ncol(Anti_Res_Genes_matrix)*unit(4, "mm"), 
                    height = nrow(Anti_Res_Genes_matrix)*unit(4, "mm"),  
                    column_title = paste("Database = ", DBs[i], sep = ""),
                    col = colorRampPalette(c("#F8696B", "#63BE7B"))(2),
                    cluster_rows = FALSE,
                    cluster_columns = FALSE,
                    top_annotation = top_annotation, 
                    left_annotation = HeatmapAnnotation(df = mlst_annotation,
                                                        which = "row",
                                                        simple_anno_size = unit(4, "mm"),
                                                        annotation_name_side = "bottom",
                                                        gap = unit(0.5, 'mm')),
                    heatmap_legend_param = list(at = c(1, 0), 
                                                labels = c("Presence", "Absence"),
                                                title = " ",
                                                color_bar = "discrete")
            ))
        }
      } else {
        draw(
          Heatmap(Anti_Res_Genes_matrix,
                  width = ncol(Anti_Res_Genes_matrix)*unit(4, "mm"), 
                  height = nrow(Anti_Res_Genes_matrix)*unit(4, "mm"),                  
                  column_title = paste("Database = ", DBs[i], sep = ""),
                  col = colorRampPalette(c("#F8696B", "#63BE7B"))(2),
                  cluster_rows = FALSE,
                  cluster_columns = FALSE,
                  top_annotation = top_annotation, 
                  heatmap_legend_param = list(at = c(1, 0), 
                                              labels = c("Presence", "Absence"),
                                              title = " ",
                                              color_bar = "discrete")
          )
        )
      }
      cat(' \n \n')
    }
  }
}
```
<br>
<br>

[Back to index](#index)

## Virulence Genes {#virulence}
<br>
```{r results='asis', warning=FALSE, message=FALSE, echo=FALSE}
if(wombat_config_json$virulence_genes$run_virulence_genes_prediction == TRUE) {
  if('abricate' %in% wombat_config_json$virulence_genes$virulence_genes_predictor_tool) {
    pander(cat("Following table(s) show(s) virulence genes by screening the draft genomes against the selected database(s) by using [ABRicate](https://github.com/tseemann/abricate). Any hit with coverage below", toString(wombat_config_json$virulence_genes$abricate$mincov), "% and identity below", toString(wombat_config_json$virulence_genes$amrfinder$minid), "% was removed.", "  \n", "<br>", "Below each column name you will find a *filter box* that you can use to filter the table by columns. You can also filter by more than one column and export this new *subset* table into a separated file (see the export buttons available)."))
  }
}
```
<br>

#### Select the database {.tabset .tabset-fade .tabset-pills}
```{r, results='asis', echo=FALSE}
if('vfdb' %in% wombat_config_json$virulence_genes$abricate$virulence_factors_databases) { 
  cat('##### VFDB\n\n')
  options("scipen" = 100, "digits" = 0)
  if(wombat_config_json$virulence_genes$run_virulence_genes_prediction == TRUE) {
    if('abricate' %in% wombat_config_json$virulence_genes$virulence_genes_predictor_tool) {
      Virulence_Genes <- 
        read_tsv(file = "Virulence_genes/Virulence_genes_ABRicate.tsv", show_col_types = FALSE) %>% 
        select(!c("COVERAGE", "COVERAGE_MAP")) %>% 
        filter(`DATABASE` == "vfdb" ) %>% 
        select(!c("DATABASE")) %>% 
        mutate(across(where(is_character), as_factor))
      Create_DT(x = Virulence_Genes, filter = "top", caption = '')
    }
  }
}
```

```{r, results='asis', echo=FALSE}
if('ecoli_vf' %in% wombat_config_json$virulence_genes$abricate$virulence_factors_databases) { 
  cat('##### ecoli_vf\n\n')
  options("scipen" = 100, "digits" = 0)
  if(wombat_config_json$virulence_genes$run_virulence_genes_prediction == TRUE) {
  if('abricate' %in% wombat_config_json$virulence_genes$virulence_genes_predictor_tool) {
    Virulence_Genes <- 
      read_tsv(file = "Virulence_genes/Virulence_genes_ABRicate.tsv", show_col_types = FALSE) %>% 
      select(!c("COVERAGE", "COVERAGE_MAP")) %>% 
      filter(`DATABASE` == "ecoli_vf" ) %>% 
      select(!c("DATABASE")) %>% 
      mutate(across(where(is_character), as_factor))
    Create_DT(x = Virulence_Genes, filter = "top", caption = '')
    }
  }
}

```
<br>

## {-}

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
if(wombat_config_json$virulence_genes$run_virulence_genes_prediction == TRUE) {
  if('abricate' %in% wombat_config_json$virulence_genes$virulence_genes_predictor_tool) {
    pander(cat("<br>", "Following figure represents presence/absence of virulence genes in each draft genome against the selected database(s) by using [ABRicate](https://github.com/tseemann/abricate). Presence is represented as minimum coverage of", toString(wombat_config_json$virulence_genes$abricate$mincov), "% and minimum identity of", toString(wombat_config_json$virulence_genes$abricate$minid), "%.", "<br>"))
  }
}
```

```{r results='asis', warning=FALSE, message=FALSE, echo=FALSE, dpi = 80}
if(wombat_config_json$virulence_genes$run_virulence_genes_prediction == TRUE) {
  if('abricate' %in% wombat_config_json$virulence_genes$virulence_genes_predictor_tool) {
    Virulence_Genes_PA <- 
      read_tsv(file = "Virulence_genes/Virulence_genes_ABRicate_matrix.tsv", show_col_types = FALSE) %>% 
      slice(-n())
    
    DBs <- levels(factor(Virulence_Genes_PA$DATABASE))
    plot_list = list()
    
    for (i in seq_along(DBs)) {
      Virulence_Genes_PA.i <- NULL
      Virulence_Genes_PA.i_data <- Virulence_Genes_PA[Virulence_Genes_PA$DATABASE == DBs[i],]
      Virulence_Genes_PA.i <- subset(Virulence_Genes_PA.i_data, select = -c(RESISTANCE, DATABASE))
      Virulence_Genes_PA.i <- as.data.frame(Virulence_Genes_PA.i)
      rownames(Virulence_Genes_PA.i) <- Virulence_Genes_PA.i$Gene
      Virulence_Genes_PA.i$Gene <- NULL
      Virulence_Genes_matrix <- t(as.matrix(Virulence_Genes_PA.i))
      
      resistance_class_annotation <- Virulence_Genes_PA.i_data[, c("Gene", "RESISTANCE")] %>% 
        select(c("RESISTANCE")) %>%
        as.data.frame
      
      if(wombat_config_json$MLST$run_mlst == TRUE) {
        Virulence_Genes_matrix <- as.data.frame(Virulence_Genes_matrix)
        Virulence_Genes_matrix <- tibble::rownames_to_column(Virulence_Genes_matrix, "Sample")
        
        Virulence_Genes_matrix_mlst <- Virulence_Genes_matrix  %>% 
          left_join(x = ., y = MLST %>% select(Sample, ST), by = "Sample")

        mlst_annotation <- Virulence_Genes_matrix_mlst %>% 
          select(., ST) %>%
          mutate(across(c(ST),
                        factor))  %>%
          as.data.frame
        
        Virulence_Genes_matrix <- as.data.frame(Virulence_Genes_matrix)
          rownames(Virulence_Genes_matrix) <- Virulence_Genes_matrix$Sample
          Virulence_Genes_matrix$Sample <- NULL
        
          plot_list[[i]] = grid.grabExpr(draw(
            Heatmap(Virulence_Genes_matrix, 
                    width = ncol(Virulence_Genes_matrix)*unit(4, "mm"), 
                    height = nrow(Virulence_Genes_matrix)*unit(4, "mm"),  
                    column_title = paste("Database = ", DBs[i], sep = ""),
                    col = colorRampPalette(c("#F8696B", "#63BE7B"))(2),
                    cluster_rows = FALSE,
                    cluster_columns = FALSE,
                    top_annotation = HeatmapAnnotation(df = resistance_class_annotation, #que solo aparezca esta anotación cuando DBs = card or ncbi.
                                                       which = "col", 
                                                       simple_anno_size = unit(4, "mm"), 
                                                       annotation_name_side = "left", 
                                                       gap = unit(1, 'mm')), 
                    left_annotation = HeatmapAnnotation(df = mlst_annotation,
                                                        which = "row",
                                                        simple_anno_size = unit(4, "mm"),
                                                        annotation_name_side = "bottom",
                                                        gap = unit(0.5, 'mm')),
                    heatmap_legend_param = list(at = c(1, 0), 
                                                labels = c("Presence", "Absence"),
                                                title = " ",
                                                color_bar = "discrete")
            )))
                    
        if(wombat_config_json$MLST$include_cc == TRUE) {
          Virulence_Genes_matrix <- as.data.frame(Virulence_Genes_matrix)
          Virulence_Genes_matrix <- tibble::rownames_to_column(Virulence_Genes_matrix, "Sample")
        
          Virulence_Genes_matrix_mlst <- Virulence_Genes_matrix  %>% 
            left_join(x = ., y = MLST %>% select(Sample, ST, `Clonal Complex`), by = "Sample")

          mlst_annotation <- Virulence_Genes_matrix_mlst %>% 
            select(., ST, `Clonal Complex`) %>%
            mutate(across(c(ST),
                          factor))  %>%
            as.data.frame
        
          Virulence_Genes_matrix <- as.data.frame(Virulence_Genes_matrix)
          rownames(Virulence_Genes_matrix) <- Virulence_Genes_matrix$Sample
          Virulence_Genes_matrix$Sample <- NULL
        
          plot_list[[i]] = grid.grabExpr(draw(
            Heatmap(Virulence_Genes_matrix, 
                    width = ncol(Virulence_Genes_matrix)*unit(4, "mm"), 
                    height = nrow(Virulence_Genes_matrix)*unit(4, "mm"),  
                    column_title = paste("Database = ", DBs[i], sep = ""),
                    col = colorRampPalette(c("#F8696B", "#63BE7B"))(2),
                    cluster_rows = FALSE,
                    cluster_columns = FALSE,
                    top_annotation = HeatmapAnnotation(df = resistance_class_annotation, #que solo aparezca esta anotación cuando DBs = card or ncbi.
                                                       which = "col", 
                                                       simple_anno_size = unit(4, "mm"), 
                                                       annotation_name_side = "left", 
                                                       gap = unit(1, 'mm')), 
                    left_annotation = HeatmapAnnotation(df = mlst_annotation,
                                                        which = "row",
                                                        simple_anno_size = unit(4, "mm"),
                                                        annotation_name_side = "bottom",
                                                        gap = unit(0.5, 'mm')),
                    heatmap_legend_param = list(at = c(1, 0), 
                                                labels = c("Presence", "Absence"),
                                                title = " ",
                                                color_bar = "discrete")
          )))
        }
      } else {
        plot_list[[i]] = grid.grabExpr(draw(
          Heatmap(Virulence_Genes_matrix,
                  width = ncol(Virulence_Genes_matrix)*unit(4, "mm"), 
                  height = nrow(Virulence_Genes_matrix)*unit(4, "mm"),                  
                  column_title = paste("Database = ", DBs[i], sep = ""),
                  col = colorRampPalette(c("#F8696B", "#63BE7B"))(2),
                  cluster_rows = FALSE,
                  cluster_columns = FALSE,
                  top_annotation = HeatmapAnnotation(df = resistance_class_annotation, #que solo aparezca esta anotación cuando DBs = card or ncbi.
                                                     which = "col", 
                                                     simple_anno_size = unit(4, "mm"), 
                                                     annotation_name_side = "left", 
                                                     gap = unit(1, 'mm')), 
                  heatmap_legend_param = list(at = c(1, 0), 
                                              labels = c("Presence", "Absence"),
                                              title = " ",
                                              color_bar = "discrete")
          )))
      }
    }
    plot_grid(plotlist = plot_list)
  }
}
```
<br>

#COMENTARIO IRENE: Se deben aproximar los valores de las columnas "% protein cover" y "% protein identity" a dos decimales

```{r results='asis', warning=FALSE, message=FALSE, echo=FALSE}
if(wombat_config_json$virulence_genes$run_virulence_genes_prediction == TRUE) {
  if('blast' %in% wombat_config_json$virulence_genes$virulence_genes_predictor_tool) {
    pander(cat("Following table shows virulence genes by screening the draft genomes against the inhouse VFDB database using [BLAST](https://pubmed.ncbi.nlm.nih.gov/10890397). Any hit with identity below __50__ % was removed.", "  \n", "<br>", "Below each column name you will find a *filter box* that you can use to filter the table by columns. You can also filter by more than one column and export this new *subset* table into a separated file (see the export buttons available)."))
  }
}

if(wombat_config_json$virulence_genes$run_virulence_genes_prediction == TRUE) {
  if('blast' %in% wombat_config_json$virulence_genes$virulence_genes_predictor_tool) {
    Virulence_Genes_Screening <- 
      read_tsv(file = "Virulence_genes/BLAST_inhouse_virulence_genes/Virulence_genes_BLAST_processed.tsv") %>% 
      relocate(Sample) %>% 
      mutate(across(where(is_character), as_factor)) %>% 
      select(!tail(names(.), 1))
    Create_DT(x = Virulence_Genes_Screening, filter = "top", caption = '')
  }
}

if(wombat_config_json$virulence_genes$run_virulence_genes_prediction == TRUE) {
  if('blast' %in% wombat_config_json$virulence_genes$virulence_genes_predictor_tool) {
    pander(cat("<br>", "Following figure represents presence/absence of virulence genes in each draft genome against the inhouse VFDB database using [BLAST](https://pubmed.ncbi.nlm.nih.gov/10890397). Presence is represented as minimum coverage of", toString(wombat_config_json$virulence_genes$blast$presence_absence_matrix$mincov), "% and minimum identity of", toString(wombat_config_json$virulence_genes$blast$presence_absence_matrix$minid), "%.", "<br>"))
  }
}
``` 

```{r results='asis', warning=FALSE, message=FALSE, echo=FALSE, dpi = 80}
if(wombat_config_json$virulence_genes$run_virulence_genes_prediction == TRUE) {
  if('blast' %in% wombat_config_json$virulence_genes$virulence_genes_predictor_tool) {
    Virulence_Genes_PA <- 
      read_tsv(file = "Virulence_genes/BLAST_inhouse_virulence_genes/Virulence_genes_BLAST_matrix.tsv", show_col_types = FALSE) %>% 
      slice(-n())
    
    Virulence_Genes_PA_matrix <- Virulence_Genes_PA  %>% 
      select(-c(Type, DATABASE)) %>%
      as.data.frame 
    
    rownames(Virulence_Genes_PA_matrix) <- Virulence_Genes_PA_matrix$Protein
    Virulence_Genes_PA_matrix$Protein <- NULL
    Virulence_Res_Genes_matrix <- t(as.matrix(Virulence_Genes_PA_matrix))
    
    virulence_class_annotation <- Virulence_Genes_PA[, c("Protein", "Type")] %>% 
        select(c("Type")) %>%
        as.data.frame
    
    if(wombat_config_json$MLST$run_mlst == TRUE) {
      Virulence_Res_Genes_matrix <- as.data.frame(Virulence_Res_Genes_matrix)
        Virulence_Res_Genes_matrix <- tibble::rownames_to_column(Virulence_Res_Genes_matrix, "Sample")
        
        Virulence_Res_Genes_matrix_mlst <- Virulence_Res_Genes_matrix  %>% 
          left_join(x = ., y = MLST %>% select(Sample, ST), by = "Sample")
      
        mlst_annotation <- Virulence_Res_Genes_matrix_mlst %>% 
          select(., ST) %>%
          mutate(across(c(ST),
                        factor))  %>%
          as.data.frame
      
        Virulence_Res_Genes_matrix <- as.data.frame(Virulence_Res_Genes_matrix)
        rownames(Virulence_Res_Genes_matrix) <- Virulence_Res_Genes_matrix$Sample
        Virulence_Res_Genes_matrix$Sample <- NULL
      
        Heatmap(Virulence_Res_Genes_matrix,
                column_names_gp = gpar(fontsize = 4),
                row_names_gp = gpar(fontsize = 4),
                width = ncol(Virulence_Res_Genes_matrix)*unit(2, "mm"), 
                height = nrow(Virulence_Res_Genes_matrix)*unit(2, "mm"),
                col = colorRampPalette(c("#F8696B", "#63BE7B"))(2),
                cluster_rows = FALSE,
                cluster_columns = FALSE,
                left_annotation = HeatmapAnnotation(df = mlst_annotation,
                                                    which = "row",
                                                    simple_anno_size = unit(4, "mm"),
                                                    annotation_name_side = "bottom",
                                                    gap = unit(0.5, 'mm')),
                top_annotation = HeatmapAnnotation(df = virulence_class_annotation,
                                                   which = "col", 
                                                   simple_anno_size = unit(4, "mm"), 
                                                   annotation_name_side = "left", 
                                                   gap = unit(1, 'mm')), 
                heatmap_legend_param = list(at = c(1, 0), 
                                            labels = c("Presence", "Absence"),
                                            title = " ",
                                            color_bar = "discrete"))
        
      if(wombat_config_json$MLST$include_cc == TRUE) {
        Virulence_Res_Genes_matrix <- as.data.frame(Virulence_Res_Genes_matrix)
        Virulence_Res_Genes_matrix <- tibble::rownames_to_column(Virulence_Res_Genes_matrix, "Sample")
        
        Virulence_Res_Genes_matrix_mlst <- Virulence_Res_Genes_matrix  %>% 
          left_join(x = ., y = MLST %>% select(Sample, ST, `Clonal Complex`), by = "Sample")
      
        mlst_annotation <- Virulence_Res_Genes_matrix_mlst %>% 
          select(., ST, `Clonal Complex`) %>%
          mutate(across(c(ST),
                        factor))  %>%
          as.data.frame
      
        Virulence_Res_Genes_matrix <- as.data.frame(Virulence_Res_Genes_matrix)
        rownames(Virulence_Res_Genes_matrix) <- Virulence_Res_Genes_matrix$Sample
        Virulence_Res_Genes_matrix$Sample <- NULL
      
        Heatmap(Virulence_Res_Genes_matrix,
                column_names_gp = gpar(fontsize = 4),
                row_names_gp = gpar(fontsize = 4),
                width = ncol(Virulence_Res_Genes_matrix)*unit(2, "mm"), 
                height = nrow(Virulence_Res_Genes_matrix)*unit(2, "mm"),
                col = colorRampPalette(c("#F8696B", "#63BE7B"))(2),
                cluster_rows = FALSE,
                cluster_columns = FALSE,
                left_annotation = HeatmapAnnotation(df = mlst_annotation,
                                                    which = "row",
                                                    simple_anno_size = unit(4, "mm"),
                                                    annotation_name_side = "bottom",
                                                    gap = unit(0.5, 'mm')),
                top_annotation = HeatmapAnnotation(df = virulence_class_annotation,
                                                   which = "col", 
                                                   simple_anno_size = unit(4, "mm"), 
                                                   annotation_name_side = "left", 
                                                   gap = unit(1, 'mm')), 
                heatmap_legend_param = list(at = c(1, 0), 
                                            labels = c("Presence", "Absence"),
                                            title = " ",
                                            color_bar = "discrete"))
      }
    } else {
      Heatmap(Virulence_Res_Genes_matrix, 
              column_names_gp = gpar(fontsize = 4), 
              row_names_gp = gpar(fontsize = 4), 
              width = ncol(Virulence_Res_Genes_matrix)*unit(2, "mm"), 
              height = nrow(Virulence_Res_Genes_matrix)*unit(2, "mm"),
              col = colorRampPalette(c("#F8696B", "#63BE7B"))(2),
              cluster_rows = FALSE,  
              top_annotation = HeatmapAnnotation(df = virulence_class_annotation,
                                                 which = "col", 
                                                 simple_anno_size = unit(4, "mm"), 
                                                 annotation_name_side = "left", 
                                                 gap = unit(1, 'mm')), 
              heatmap_legend_param = list(at = c(1, 0), 
                                          labels = c("Presence", "Absence"),
                                          title = " ",
                                          color_bar = "discrete"))
    }
  }
}
```
<br>

[Back to index](#index)

## Plasmids {#plasmid}
<br>
```{r results='asis', warning=FALSE, message=FALSE, echo=FALSE}
if(wombat_config_json$plasmids$run_plasmid_prediction == TRUE) {
  plasmids_data <- read_tsv(file = "Plasmids/Plasmids_ABRicate_plasmidfinder.tsv", show_col_types = FALSE) %>% 
      slice(-n())
  if (nrow(plasmids_data) == 0) {
    cat("No plasmids found in any of the draft genomes.")
  } else {
    pander(cat("Following table(s) show(s) plasmids by screening the draft genomes against PlasmidFinder by using [ABRicate](https://github.com/tseemann/abricate). Any hit with coverage below", toString(wombat_config_json$plasmids$abricate$mincov), "% and identity below", toString(wombat_config_json$plasmids$abricate$minid), "% was removed.", "  \n", "<br>", "Below each column name you will find a *filter box* that you can use to filter the table by columns. You can also filter by more than one column and export this new *subset* table into a separated file (see the export buttons available)."))
  }
}
```
<br>

```{r results='asis', warning=FALSE, message=FALSE, echo=FALSE}
if(wombat_config_json$plasmids$run_plasmid_prediction == TRUE) {
  plasmids_data <- read_tsv(file = "Plasmids/Plasmids_ABRicate_plasmidfinder.tsv", show_col_types = FALSE) %>% 
      slice(-n())
  if (nrow(plasmids_data) > 0) {
    Create_DT(x = plasmids_data, filter = "top", caption = '')
  }
}
```
<br>

[Back to index](#index)

## Pangenome analysis {#pangenome}
<br>
```{r results='asis', warning=FALSE, message=FALSE, echo=FALSE}
if(wombat_config_json$pangenome$run_pangenome == TRUE) {
  pander(cat("Following charts show pangenome analysis with minimum", toString(wombat_config_json$pangenome$minid),
  "% identity for blastp using [Roary](https://pubmed.ncbi.nlm.nih.gov/26198102).", "  \n", "<br>"))
}

if(wombat_config_json$pangenome$run_pangenome == TRUE) {
  Pangenome_genes_summary <- 
    read_delim(file = "Roary_pangenome/summary_statistics.txt", delim = "\t", col_names = FALSE, escape_double = FALSE, trim_ws = TRUE, show_col_types = FALSE) %>% 
    filter(`X3` != "0" ) %>%
    mutate(across(where(is_character), as_factor)) %>% 
    slice(., 1:(n() - 1)) %>% 
    mutate(percentage = `X3`/sum(`X3`)*100)  %>% 
    mutate(across(percentage, round, 0))
  
  #First figure: pangenome summary statistics pie chart
  Pangenome_genes_summary %>%  ggplot(data = ., 
                                             aes(x = "", y = .[[3]], fill = .[[1]])) +
    geom_bar(stat = "identity", width = 1, color="white") +
    coord_polar("y", start = 0) + 
    labs(fill = "") +
    scale_fill_brewer(palette = "Blues") +
    theme_minimal() +
    ggtitle("Breakdown of genes in percentage") +
    theme(
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      panel.border = element_blank(),
      panel.grid = element_blank(),
      axis.ticks = element_blank(),
      axis.text.x = element_blank(),
      plot.title = element_text(size = 12, hjust = 0.5, face = "bold"),
  ) +
    geom_label(aes(label = percentage),
               color = "black",
               position = position_stack(vjust = 0.5),
               show.legend = FALSE)
}
```
<br>

```{r results='asis', warning=FALSE, message=FALSE, echo=FALSE}
if(wombat_config_json$pangenome$run_pangenome == TRUE) {
  #Second figure: pangenome frequency
  Pangenome_frequency <- 
    readr::read_csv(file = "Roary_pangenome/gene_presence_absence.csv", show_col_types = FALSE) %>% 
    dplyr::mutate(across(where(is_character), as_factor)) %>% 
    dplyr::select(.data = ., c(1, 15:last_col())) 

  Pangenome_frequency_Genomes <-
    Pangenome_frequency %>% 
    select(-1) %>% 
    dplyr::mutate(across(where(is_character), as_factor)) %>% 
    dplyr::mutate(across(where(is.factor), as.numeric)) %>% 
    mutate_all(~ +(. > 0)) %>% 
    dplyr::transmute(Genomes = rowSums(., na.rm = TRUE))

  Pangenome_frequency$Genomes <- Pangenome_frequency_Genomes$Genomes
  
  Pangenome_frequency %>% 
    ggplot(data = ., aes(x = Genomes)) +
    geom_bar(stat = "count") +
    theme_classic() +
    ggtitle("Frequency of genes versus the number of genomes") +
    labs(x = "Number of genomes", y = "Number of genes") +
    theme(
      legend.position = "right",
      plot.title = element_text(size = 12, hjust = 0.5, face = "bold"),
  )
}
```
<br>

```{r results='asis', warning=FALSE, message=FALSE, echo=FALSE}
if(wombat_config_json$pangenome$run_pangenome == TRUE) {
  #Third figure: phylogenetic tree
  tree <- ape::read.tree(file = "Roary_pangenome/accessory_binary_genes.fa.newick")
  ggtree(tree, size=1/5) + #Size refers to thickness of branches
    ggtitle("Phylogenetic tree based on presence/absence of accesory genes") +
    geom_tiplab(size=4,
                align=FALSE,  #Align tree labels to the end of each leaf
                linesize=0.5) + #line size of line if align = TRUE
    geom_treescale(offset = -0.2) +
    theme(plot.title = element_text(size = 12, hjust = 0.5, face = "bold")) +
    coord_cartesian(clip="off") #prevents labels from being clipped off
}
```
<br>

```{r results='asis', warning=FALSE, message=FALSE, echo=FALSE}

if(wombat_config_json$pangenome$run_pangenome == TRUE) {
  #Foruth figure: pangenome with phylogenetic tree 
  cat("Binary heatmap shows the presence (dark grey) and absence (white) of genes. Phylogeny for each isolate is shown on the left and was constructed based on accesory genes from the pangenome.", "<br>")
  pangenome <- read_delim(file = "Roary_pangenome/gene_presence_absence.Rtab", delim = "\t", show_col_types = FALSE) %>%
  mutate(across(where(is_character), as_factor)) %>%
  t(.)  %>%
  as.data.frame()

  names(pangenome) <- pangenome[1,]
  pangenome <- as.matrix(pangenome[-1,])
  class(pangenome) <- "numeric"

  tree <- ape::read.tree(file = "Roary_pangenome/accessory_binary_genes.fa.newick")
  tree_graph <- ggtree(tree, size=1/5) + #Size refers to thickness of branches
    geom_tiplab(size=4,
                align=FALSE,  #Align tree labels to the end of each leaf
                linesize=0.5) + #line size of line if align = TRUE
    geom_treescale(offset = -0.2)

  phylo.heatmap(as.phylo(tree_graph),
                pangenome,
                colors=colorRampPalette(colors=c("white","grey"))(2),
                labels=F,
                pts=FALSE, #draw tip labs in tree
                lwd=2, #thickness of lines in tree
                split=c(0.5,1) #space for tree and matrix
              )
}
```
<br>

[Back to index](#index)

## Genomic variants {#variants}
<br>
```{r results='asis', warning=FALSE, message=FALSE, echo=FALSE}
if(wombat_config_json$MLST$run_mlst == TRUE) {
  cat("Following table shows genomic variants in each draft genome against the reference genome you indicated using [Snippy](https://github.com/tseemann/snippy).", "  \n", "<br>", "Below each column name you will find a *filter box* that you can use to filter the table by columns. You can also filter by more than one column and export this new *subset* table into a separated file (see the export buttons available).")
  Genomic_variants <- 
    read_tsv(file = "SNP_SNIPPY/Genomic_variants_summary.tsv", show_col_types = FALSE) %>% 
    relocate(Sample) %>%
    mutate(Sample = as.factor(Sample)) %>%
    left_join(x = ., y = MLST %>% select(Sample, ST, `Clonal Complex`), by = "Sample")
} else {
  Genomic_variants <- 
    read_tsv(file = "SNP_SNIPPY/Genomic_variants_summary.tsv", show_col_types = FALSE) %>% 
    relocate(Sample)
}
Create_DT(x = Genomic_variants, filter = "top", caption = '')
```
<br>

[Back to index](#index)

## Summary report {#summary}
<br>
```{r results='asis', warning=FALSE, message=FALSE, echo=FALSE}
cat("Following table shows summary information for each draft genome.", "  \n", "<br>", "Below each column name you will find a *filter box* that you can use to filter the table by columns. You can also filter by more than one column and export this new *subset* table into a separated file (see the export buttons available).")
summary_draft_genome <- 
  read_tsv(file = "wombat_report.csv", show_col_types = FALSE) %>% 
  relocate(Sample) %>% 
  rename(`Clonal Complex` = clonal_complex) %>%
  mutate(across(where(is_character), as_factor))

Create_DT(x = summary_draft_genome, filter = "top", caption = '')
```
<br>

[Back to index](#index)

## How to citate {#citation}
<br>
Irene Ortega-Sanz, Jose A. Barbero and Antonio Canepa. __Wombat__ (2022). Available at [https://github.com/JoseBarbero/Wombat](https://github.com/JoseBarbero/Wombat)
<br>
<br>


Following packages and tools were used in Wombat:

| Package/Tool      | Reference   | 
|-------------------|-------------|
| Trimmomatic       | [A.M. Bolger et al., 2014](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4103590/)   |
| Prinseq           | [R. Schmieder and R. Edwards, 2011](https://www.ncbi.nlm.nih.gov/pubmed/21278185)   |
| FLASH             | [T. Magoc and S. Salzberg, 2011](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3198573/) |
| SPAdes            | [A. Bankevich et al., 2012](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3342519/) |
| QUAST             | [A. Gurevich et al., 2013](https://www.ncbi.nlm.nih.gov/pubmed/23422339) |
| progressiveMauve  | [A.E. Darling et al., 2010](https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0011147) |
| mlst              | [T. Seemann](https://github.com/tseemann/mlst) |
| Abricate          | [T. Seemann](https://github.com/tseemann/abricate) |
| BLAST             | [Z. Zhang et al., 2000](https://www.ncbi.nlm.nih.gov/pubmed/10890397)
| AMRFinderPlus     | [M. Feldgarden et al., 2019](https://journals.asm.org/doi/10.1128/AAC.00483-19) |
| Prokka            | [T. Seemann, 2014](https://www.ncbi.nlm.nih.gov/pubmed/24642063) |
| DFAST             | [Y. Tanizawa et al., 2018](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5860143/) |
| Roary             | [A.J. Page et al., 2015](https://www.ncbi.nlm.nih.gov/pubmed/26198102) |
| snippy            | [T. Seemann](https://github.com/tseemann/snippy) |
| rmarkdown         | [Allaire et al., 2021](https://cran.r-project.org/web/packages/rmarkdown/index.html) |
| tidyverse         | [Wickham et al., 2019](https://tidyverse.tidyverse.org/) |
| ComplexHeatmap    | [Gu, 2016](https://www.bioconductor.org/packages/release/bioc/html/ComplexHeatmap.html) |
| DT                | [Xie et al., 2021](https://cran.r-project.org/web/packages/DT/index.html) |
| ggrepel           | [Slowikowski, 2021](https://cran.r-project.org/web/packages/ggrepel/) |
| plotly            | [Sievert, 2020](https://cran.r-project.org/web/packages/plotly/index.html) |
| rjson             | [Couture-Beil, 2018](https://cran.r-project.org/web/packages/rjson/index.html) |
| scales            | [Wickham and Seidel, 2020](https://cran.r-project.org/web/packages/scales/index.html) |
| viridis           | [Garnier et al., 2021](https://cran.r-project.org/web/packages/viridis/index.html) |

[Back to index](#index)
